ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-02-27 pyked.tex
added additional CloudFlame refs

Despite the development of these standards, limited examples of open data
\emph{sharing} using the formats exist in the literature. To the best
of our knowledge, the largest such publicly available database is hosted by
the Clean Combustion Research Center at King Abdullah University of Science and
Technology (KAUST) and is known as CloudFlame
(\url{https://cloudflame.kaust.edu.sa}). Started in
2013~\autocite{Goteng:2013cf},\todo{a few more refs needed}{} CloudFlame serves
as an openly accessible database for experimental data, available in a standard
CSV format, and also provides a cloud infrastructure for running simulations
based on stored models and data. While an admirable and useful effort,
CloudFlame, like ReSpecTh and PrIMe, is a closed system controlled by a single
institution rather than by the community at large.

>>>>

Despite the development of these standards, limited examples of open data
\emph{sharing} using the formats exist in the literature. To the best
of our knowledge, the largest such publicly available database is hosted by
the Clean Combustion Research Center at King Abdullah University of Science and
Technology (KAUST) and is known as CloudFlame
(\url{https://cloudflame.kaust.edu.sa}). Started in
2013~\autocite{Goteng:2013cf,Goteng:2014,ReynoChiasson:2015}, CloudFlame serves
as an openly accessible database for experimental data, available in a standard
CSV format, and also provides a cloud infrastructure for running simulations
based on stored models and data. While an admirable and useful effort,
CloudFlame, like ReSpecTh and PrIMe, is a closed system controlled by a single
institution rather than by the community at large.
